Classical Simulation of Quantum Error Correction in a Fibonacci Anyon Code

### 2015-06-11 fib2.tex
near-final draft?
Version 1.0!  Woohoo!

\begin{figure}[t!]
\begin{center}
    \includegraphics[]{pic-braid-loop.pdf}
\caption{
%The perspective of TQFT.
The deformation of observables corresponding to the implementation of a braid process on three anyons is shown. The configurations before and after are connected by world lines shown in red, while the observable Wilson loops are shown in black.
%Here we show the world lines of a braid.
%This braid relates two different ways of observing the same charges.
%In this case, we see how it relates two different ways of observing (or fusing) the top two charges.
This process relates two different ways of observing (or fusing) the top two charges.
%This braid relates two different ways of observing the same charges.
%We are free to draw these loops around charges,
In general, braiding will wind or unwind the Wilson loops, following
the deformation of the manifold itself.
\label{f:braidloop}
}
\end{center}
\vspace{-10pt}
\end{figure}

@@

Observables associated to non-intersecting loops commute, and so
a basis for the space can be built from a maximal
set of disjoint, nested loops.
For three anyons, two
possible ways of nesting loops are related
via $F$-moves:
\begin{align}
\label{e:fmove}
\includegraphics[]{pic-fmove.pdf}
\end{align}
Here we have shown particles with charges $a$, $b$, and $c$
as well as total charge $d$.
The lefthand side shows a state where the anyons with charge $a$ and $b$ are
observed to have total charge $i$.
The righthand side involves a superposition 
over total charge $j$ of the anyons with charge $b$ and $c$. 
The green line serves to linearly
order the anyons, and track
deformations in the underlying space, 
i.e.\ the history of braiding processes.
It also denotes the direction along
which $F$-moves occur. A clockwise braiding process is represented by an $R$-move:
\begin{align}
\label{e:rmove}
\includegraphics[]{pic-rmove.pdf}
\end{align}
%This is meant to show a \emph{half-twist} of the space
%inside the observable with value $c$
%holding two anyons (punctures) with charges $a$ and $b$. \cggb{This statement isn't quite true. I suggest just deleting.}

@@

In order to track the state of the system we maintain 
a set of disjoint directed curves, 
one for each connected component with trivial total charge.
Unlike previous work~\cite{Brell2013}, this creates a dynamically generated basis for the fusion space 
that easily allows for tensor factorization of disjoint components.
The application of a pair-creation noise process corresponds to the 
addition of an extra curve to the lattice, supporting
two new anyons.
%along with two preferred points on it denoting the anyon locations. 
Following the noise processes, our simulation must %proceed to 
measure the total charge within each tile; the results of 
these measurements will form the error syndrome. 
This requires joining (arbitrarily) any curves that intersect that tile, 
and then performing $R$- and $F$-moves on the resulting
curve so that 
all anyons within the tile have been 
localized within a contiguous region of the curve. 
%\dude{Heisenberg picture?}
%The observable corresponding to the tile is then
%represented in the state \dude{polish}.
%The total charge is then (probabilistically) read off the 
%relevant section of the fusion tree. 
An example of this 
procedure for a simple noise process is shown in \Fref{f:syndrome}.
%and the corresponding braid moves are shown in \Fref{f:syndrome}(e).
The combinatorial derivation of the algorithm and data structures used for 
this procedure will be discussed elsewhere.
Braiding processes that encircle 
a non-trivial loop of our (toric) manifold can also be 
treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
\cggb{what does the combinatorial comment mean?}
\cggb{why did the Pfeifer ref get commented? it should certainly go somewhere.}
%\cggb{This paragraph and the next still needs another look.}

@@

We have demonstrated classical simulation of successful error correction in a universal anyon model. 
Though we have chosen several properties of our model and 
simulation in a convenient way for simplicity,
Ref.~\cite{Brell2013} presents good evidence that it is
unlikely these choices will affect our results qualitatively.
%it seems highly
%unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}. 
In particular, although we have modeled our logical qubit as 
encoded in the global topological degrees of freedom of our 
system, we could have encoded it in the fusion space of several preferred anyons. 
This situation would be appropriate to model error-correction routines for topological quantum computation. 
Additionally, we expect our results to be stable to changes in details of the noise model and decoding algorithm.

>>>>

\begin{figure}[t!]
\begin{center}
    \includegraphics[]{pic-braid-loop.pdf}
\caption{
%The perspective of TQFT.
The deformation of observables corresponding to the implementation of a braid process on three anyons is shown. The configurations before and after are connected by world lines shown in red, while the observable Wilson loops are shown in black.
%Here we show the world lines of a braid.
%This braid relates two different ways of observing the same charges.
%In this case, we see how it relates two different ways of observing (or fusing) the top two charges.
This process relates two different ways of observing (or fusing) the top two charges.
%This braid relates two different ways of observing the same charges.
%We are free to draw these loops around charges,
In general, braiding will twist these loops in different ways following
the deformation of the manifold itself.
\label{f:braidloop}
}
\end{center}
\vspace{-10pt}
\end{figure}

@@

Observables associated to non-intersecting loops commute, and so
a basis for the space can be built from a maximal
set of disjoint, nested loops.
For three anyons, two
possible ways of nesting loops are related
via $F$-moves:
\begin{align}
\label{e:fmove}
\includegraphics[]{pic-fmove.pdf}
\end{align}
Here we have shown particles with charges $a$, $b$, and $c$
as well as total charge $d$.
The lefthand side shows a state where the anyons with charge $a$ and $b$ are
observed to have total charge $i$.
The righthand side involves a superposition 
over total charge $j$ of the anyons with charge $b$ and $c$. 
The green line serves to linearly
order the anyons, and track
deformations in the underlying space, 
i.e.\ the history of braiding processes.
It also denotes the direction along
which $F$-moves occur. A clockwise braiding process, or \emph{half-twist}, is effected by an $R$-move:
\begin{align}
\label{e:rmove}
\includegraphics[]{pic-rmove.pdf}
\end{align}
%This is meant to show a \emph{half-twist} of the space
%inside the observable with value $c$
%holding two anyons (punctures) with charges $a$ and $b$. \cggb{This statement isn't quite true. I suggest just deleting.}

@@

In order to track the state of the system we maintain 
a set of disjoint directed curves, 
one for each connected component with trivial total charge.
Unlike previous work~\cite{Brell2013}, this creates a dynamically generated basis for the fusion space 
that allows for tensor factorization of disjoint components.
The application of a pair-creation noise process corresponds to the 
addition of an extra curve to the lattice, supporting
two new anyons.
%along with two preferred points on it denoting the anyon locations. 
Following the noise processes, our simulation must %proceed to 
measure the total charge within each tile; the results of 
these measurements will form the error syndrome. 
This requires joining (arbitrarily) any curves that intersect that tile, 
and then performing $R$- and $F$-moves on the resulting
curve so that 
all anyons within the tile have been 
localized within a contiguous region of the curve. 
%\dude{Heisenberg picture?}
%The observable corresponding to the tile is then
%represented in the state \dude{polish}.
%The total charge is then (probabilistically) read off the 
%relevant section of the fusion tree. 
An example of this 
procedure for a simple noise process is shown in \Fref{f:syndrome}.
%and the corresponding braid moves are shown in \Fref{f:syndrome}(e).
The details of the algorithm and data structures used for 
this procedure will be discussed elsewhere.
Braiding processes that encircle 
a non-trivial loop of our (toric) manifold can also be 
treated in an analogous way, following e.g.~\cite{Pfeifer2012}.
%\cggb{what does the combinatorial comment mean?}
%\cggb{why did the Pfeifer ref get commented? it should certainly go somewhere.}
%\cggb{This paragraph and the next still needs another look.}

@@

We have demonstrated classical simulation of successful error correction in a universal anyon model. 
Though we have chosen several properties of our model and 
simulation in a convenient way for simplicity,
Ref.~\cite{Brell2013} presents good evidence that it is
unlikely these choices will affect our results qualitatively.
%it seems highly
%unlikely that they will affect the qualitative results, similarly to the results of Ref.~\cite{Brell2013}. 
In particular, although we have modeled our logical qubit as 
encoded in the global topological degrees of freedom of our 
system, we could have encoded it in the fusion space of several preferred anyons. 
This situation would be appropriate to model error-correction routines for topological quantum computation. 
Additionally, we expect our results to be stable to changes in details of the noise model and decoding algorithm, again following Ref.~\cite{Brell2013}.
